\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-26 coq-example.tex
Fix and Reply the comments.

Most of the proof is directly adapted
from the one in Software Foundation, resulting in a similarly accessible proof, while the proof for each extended feature are scattered in the extended families resulting better modularity. One kind of examples are about the computation, and here we mainly focus on substitution functions. Substitutions dealing with product and projection are defined in the corresponding children family. This is mainly done by inheriting and extending the handler family from the parents. The other kind of examples are about proof-irrelevant propositions and we directly use "(Extend) FTheorem" to handle them. In these cases we don't even to additionally handle a auxillary handler family like we did for substitution---we simply use "Extend FTheorem"

For example, the proof on progress on product projection is carried out in the children family that extend "tm" with products.

\YZ{Can you say more about how your plugin enables more code reuse and modularity?}
% In related work, Coq/Metatheory a la carte/Tion embedding can be emphasized as a more "semantic approach" because they encode the meaning using a special design pattern (for example, open recursive inductive type for extension), compared to our more syntactic approach. Their advantage is the transferability of this technique accross different proof assistants, and their disadvantage is that their approach are less accessible and unfriendly to amateur Coq users---which can be reflected from the distance of their approach and text-book Software Foundation proof.

@@

The first family "Lang" define the big step operator (using fuel) of a
while language, with expression. But it postulates the computational
information of "State" (environment mapping) used by Lang. It takes about 200+ LOCs. 
% We
% can
\YZ{In general, in a result section like this, you want to show what
you *have done* rather than what you *can do*.}\EDJreply{Ok. deleted. I initially want to emphasize ``I **can** use arbitrary implementation for this environment mapping interface'' but I don't know how to say that without using ``can''.}
% swap the implementation of "State" to have different memory/state
% management by extending family "Lang".
\YZ{What is 'different
memory/state management'?}\EDJreply{Actually I should say environment mapping/dictionary. I instantiate it with function(closure) as environment mapping in "LangRun". It is possible to use other mapping like Coq's primitive dictionary.}

>>>>

Most of the proof and computation is directly adapted
from the one in Software Foundation, resulting in a similarly accessible proof, while the proof for each extended feature are scattered in the extended families resulting better modularity. One kind of examples is about the computation, and here we mainly focus on substitution functions. Substitutions dealing with product and projection are defined in the corresponding children family. This is mainly done by inheriting and extending the handler family from the parents. The other kind of examples are about proof-irrelevant propositions and we directly use "(Extend) FTheorem" to handle them. In these cases we don't even need to additionally handle a auxillary handler family like we did for substitution---we simply use "Extend FTheorem" and our plugin will prepare the goal to prove. At the end, it will look like scattered proof scripts in a modular manner.
For example, the proof on progress on product projection is carried out in the children family that extend "tm" with products. \YZ{Can you say more about how your plugin enables more code reuse and modularity?}\EDJreply{please check}
% In related work, Coq/Metatheory a la carte/Tion embedding can be emphasized as a more "semantic approach" because they encode the meaning using a special design pattern (for example, open recursive inductive type for extension), compared to our more syntactic approach. Their advantage is the transferability of this technique accross different proof assistants, and their disadvantage is that their approach are less accessible and unfriendly to amateur Coq users---which can be reflected from the distance of their approach and text-book Software Foundation proof.

@@

The first family "Lang" define the big step operator (using fuel) of a
while language, with expression. However, it postulates the definition of "State" (environment mapping) used by Lang. It takes about 200+ LOCs. 
% We
% can
\YZ{In general, in a result section like this, you want to show what
you *have done* rather than what you *can do*.}\EDJreply{Ok. deleted. I initially want to emphasize ``I **can** use arbitrary implementation for this environment mapping interface'' but I don't know how to say that without using ``can''.}
% swap the implementation of "State" to have different memory/state
% management by extending family "Lang".
\YZ{What is 'different
memory/state management'?}\EDJreply{Actually I should say environment mapping/dictionary. I instantiate it with function(closure) as environment mapping in "LangRun". It is possible to use other mapping like Coq's primitive dictionary.}

### 2022-06-26 coqimpl.tex
Fix and Reply the comments.

Since it is possible to consider inheritance as solely a first-order data rather
than a higher-order functor, it is possible to
\text{mix-in} two inheritance data---by carefully ``mix'' the internal list.However, a good definition of mixin is still under investigation.\YZ{How about making mixin composition one of your Req's? Also does any example in the paper illustrate how to do this?}\EDJreply{mixin is not really formalized. There is no example illustrate it. The only example is the STLC example at the very end and I just kind of ``mention'' it. I think here I just want to emphasize, inheritance as first order data is still possible to support composition.}

@@

% Insert one pseudo-code example for explanation of the mechanism
% Use the natural number example
\begin{figure}[!htb]
  \begin{minipage}[t]{0.3\linewidth}
\begin{minted}[fontsize=\footnotesize,escapeinside=@@]{Coq}
Family B.
  FInductive b : Set 
    := tt : b | ff : b.
  Family neg_handler. 
    Field tt : self_B.b 
      := self_B.ff.
    Field ff : self_B.b 
      := self_B.tt.
  EndFamily.
FRecursor neg 
  about self_B.b 
  motive (fun _ => self_B.b)
  using self_B.neg_handler
  by _rec.
EndFamily.

@@

Let's look at \cref{fig:plugin-example2}, the example of boolean and
negation. When we define inductive type "b", the following "Field
neg_handler.ff" can only know "b" is a type (of "Set") and there are at
least two constructors for it, just like what we declare in ``the
abstracted interface'' the compiled module type "b_3". We cannot export\YZ{export or put?}\EDJreply{Ok. I just figure out how my wording is confusing. put is absolutely correct but by put I want to mean ``export''. I think I use ``export'' in several places...}
the eliminator of "b" inside "b_3" because doing so "neg_handler.ff"
(and "ff_24") will not be able to be inherited to the context where "b"
is extended with a third constructor, since the existence of recursor
alone will assert that there are only two constructors in "b", not
``extensible'' at all!\YZ{I can see how the existence of the recursor alone prevents extensibility, but I don't see why it has to do with ff_24.}

@@

To construct a recursor as in \ref{langdesign-req3}, we create for each
constructor a handler and aggregate them inside a family. The whole
family "neg_handler" can be considered as a large matching case. Doing
so, family inheritance can function as matching-case reuse. Then we use
"FRecursor" to specify the motive and inductive type. Here "FRecursor"
will feed Coq
a module "v_33_34" for doing type-checking---what it does is basically
assert the existence of the recursor and apply to see if handlers can
pass the type checking by Coq.

Since the recursor is constructed knowing a concrete inductive type,
thus not inheritable, for all the children, we have to reconstruct and
override with a new recursor (therefore serving as exhaustiveness
checking for child families). This is affordable since each recursor handler doesn't need
to be rechecked---look at "B2.neg_handler", there is only one new
handler for "uu" and the handlers from the parent
"B.neg_handler.tt,B.neg_handler.ff" have already been type-checked and
inherited (thanks to the fact that they only rely on ``the abstracted
interface'' module "b_3"). Of course, our plugin will ``inherit'' the
recursor "neg" but what the plugin does is doing exhaustiveness
checking, again.\YZ{It'd be good to show *concretely* in Figure 4
(1) code that uses the recursor and how the using code is compiled, (2)
how B2 is compiled and that compiling B2 does not require recompiling
fields inherited from B.}

@@

Thus to refer to them, we have to scope the defining tactic with "MetaData" and our plugin will setup the appropriate environment. After a "MetaData" block is closed, the plugin will aggregate the content into the current defining family so that they can also be used when defining the following fields of the family. This can fulfill \ref{langdesign-req5}.\YZ{Consider adding examples of Closing Fact and MetaData, even if only to be included in an appendix.}

>>>>

Though inheritance is solely a first-order data rather
than a higher-order functor, it is still possible to
\text{mix-in} two inheritance data---by carefully ``mix'' the internal list, we can compose the inheritance. However, a good definition of mixin is still under investigation.\YZ{How about making mixin composition one of your Req's? Also does any example in the paper illustrate how to do this?}\EDJreply{mixin is not really formalized. There is no example illustrate it. The only example is the STLC example at the very end and I just kind of ``mention'' it. I think here I just want to emphasize, inheritance as first order data is still possible to support composition.}

@@

% Insert one pseudo-code example for explanation of the mechanism
% Use the natural number example
\begin{figure}[!htb]
  \begin{minipage}[t]{0.32\linewidth}
\begin{minted}[fontsize=\footnotesize,escapeinside=@@]{Coq}
Family B.
  FInductive b : Set 
    := tt : b | ff : b.
  Family neg_handler. 
    Field tt : self_B.b 
      := self_B.ff.
    Field ff : self_B.b 
      := self_B.tt.
  EndFamily.
  FRecursor neg 
    about self_B.b 
    motive (fun _ => self_B.b)
    using self_B.neg_handler
    by _rec.
  Field example := 
    self_B.neg self_B.tt. 
EndFamily.

@@

Let's look at \cref{fig:plugin-example2}, the example of boolean and
negation. When we define inductive type "b", the following "Field
neg_handler.ff" can only know "b" is a type (of "Set") and there are at
least two constructors for it, just like what we declare in ``the
abstracted interface'' the compiled module type "b_3". We cannot export\YZ{export or put?}\EDJreply{Ok. I just figure out how my wording is confusing. put is absolutely correct but by put I want to mean ``export''. I think I use ``export'' in several places...}
the eliminator of "b" inside "b_3" because doing so all of the following fields (e.g. "neg_handler.ff" and the corresponding "ff_24") will not be able to be inherited to the context where "b"
is extended with a third constructor, since the existence of recursor
alone will assert that there are only two constructors in "b", not
\textbf{extensible} at all!\YZ{I can see how the existence of the recursor alone prevents extensibility, but I don't see why it has to do with ff_24.}\EDJreply{You are right. It is not only about "ff_24".I rephrased it. Please check.}

@@

To construct a recursor as in \ref{langdesign-req3}, we create for each
constructor a handler and aggregate them inside a family. The whole
family "neg_handler" can be considered as a large matching case. 
Then we use
"FRecursor" to specify the motive and inductive type. Here "FRecursor"
will feed Coq
a module "v_33_34" for doing type-checking---what it does is basically
assert the existence of the recursor and apply to see if handlers can
pass the type checking by Coq.

Once recursor is created it will look like any other function fields (and compiled in the same manner), here we show "self_B.neg" to apply to "self_B.tt" for "B.example".  While in the implementation of our plugin, the concrete recursor for this "neg" will only be created during the compilation of the surrounding family into module---it will look exactly "term_for_type_checking" but uses concrete recursor. For example, at the appropriate place, our plugin will insert a definition into the compiled module: 
\begin{minted}{Coq}
  Definition neg := b_rec (fun _ => b) neg_handler.tt neg_handler.ff.
\end{minted}
where "b_rec" and "b" are the corresponding recursor and the (vanilla) inductive type in that compiled module.

Since the recursor is constructed knowing a concrete inductive type,
thus not inheritable, for all the children, we have to reconstruct and
override with a new recursor (therefore serving as exhaustiveness
checking for children families). 
This is affordable since each recursor handler doesn't need
to be rechecked---look at "B2.neg_handler", there is only one new
handler for "uu" and the handlers from the parent
"B.neg_handler.tt,B.neg_handler.ff" have already been type-checked and
inherited (since they only rely on ``the abstracted
interface'' module "b_3"). 
Thanks to family inheritance, their corresponding compiled module from the parents---for example, 
the module "ff_24"---doesn't require another type-check and is re-used during the type-checking and compilation of "B2.neg".

Of course, our plugin will ``inherit'' the
recursor "neg" in the surface 
but what the plugin does is doing a second exhaustiveness
checking in children family.\YZ{It'd be good to show *concretely* in Figure 4
(1) code that uses the recursor and how the using code is compiled, (2)
how B2 is compiled and that compiling B2 does not require recompiling
fields inherited from B.}\EDJreply{I added both. Please check.}

@@

Thus to refer to them, we have to scope the defining tactic with "MetaData" and our plugin will setup the appropriate environment. After a "MetaData" block is closed, the plugin will aggregate the content into the current defining family so that they can also be used when defining the following fields of the family. This can fulfill \ref{langdesign-req5}.\YZ{Consider adding examples of Closing Fact and MetaData, even if only to be included in an appendix.}\EDJreply{Added. Please check}
